### 2020-02-23 main_text/main_text.tex
Update author list & acknowledgements

	% Title must be 250 characters or less.
	\begin{flushleft}
		{\Large
			\textbf\newline{Theoretical investigation of a genetic switch for metabolic adaptation} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
		}
		\newline
		% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
		\\
		Kathrin S. Laxhuber\textsuperscript{1},
		Muir J. Morrison\textsuperscript{2},
		Rob Phillips\textsuperscript{2,3$\ast$}
		\\
		\bigskip
		\textbf{1} Department of Chemistry and Applied Biosciences, ETH Zurich, 8093 Zurich, Switzerland
		\\
		\textbf{2} Department of Physics, California Institute of Technology, Pasadena, CA, USA
		\\
		\textbf{3} Division of Biology and Biological Engineering, California Institute of Technology, Pasadena, CA, USA
		\\
		\bigskip

@@

	\section*{Acknowledgments}
	We thank Griffin Chure, Charlotte Strandkvist, and Kyle Naughton for
	providing their data on the \emph{xap} system and pointing out the
	bistability. We also thank Griffin Chure for answering the many biological
	questions that arose, Nathan Belliveau for bringing similar systems to our
	attention, Patrick Lenggenhager for his help with \emph{Mathematica} issues, and Jane Kondev and Jin Wang for interesting discussions.
	For assistance with illustrations, we also thank Nigel Orme and Griffin Chure.
	This work was supported by 1R35 GM118043-01 Maximizing Investigators'
	Research Award (MIRA) (to R.P.), and the Werner Siemens Foundation
	through the Swiss Study Foundation (K.S.L.). This material is based upon
	work supported by the National Science Foundation Graduate Research
	Fellowship under Grant No.\ DGE-1745301 (M.J.M.).

>>>>

	% Title must be 250 characters or less.
	\begin{flushleft}
		{\Large
			\textbf\newline{Theoretical investigation of a genetic switch for metabolic adaptation} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
		}
		\newline
		% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
		\\
		Kathrin S. Laxhuber\textsuperscript{1},
		Muir J. Morrison\textsuperscript{2},
		Griffin Chure\textsuperscript{3},
		Rob Phillips\textsuperscript{2,3$\ast$}
		\\
		\bigskip
		\textbf{1} Department of Chemistry and Applied Biosciences, ETH Zurich, 8093 Zurich, Switzerland
		\\
		\textbf{2} Department of Physics, California Institute of Technology, Pasadena, CA, USA
		\\
		\textbf{3} Division of Biology and Biological Engineering, California Institute of Technology, Pasadena, CA, USA
		\\
		\bigskip

@@

	\section*{Acknowledgments}
	Portions of the experiments reported here were carried out at the
	Physiology summer course at the Marine Biological Laboratory in Woods
	Hole, MA, operated by the University of Chicago. We thank Charlotte
	Strandkvist and Kyle Naughton for their work on the project during the
	course. We also Nathan Belliveau for strain creation work and for
	bringing similar systems to our
	attention, Patrick Lenggenhager for his help with \emph{Mathematica} issues, and Jane Kondev and Jin Wang for interesting discussions.
	For assistance with illustrations, we also thank Nigel Orme.
	This work was supported by 1R35 GM118043-01 Maximizing Investigators'
	Research Award (MIRA) (to R.P.), and the Werner Siemens Foundation
	through the Swiss Study Foundation (K.S.L.). This material is based upon
	work supported by the National Science Foundation Graduate Research
	Fellowship under Grant No.\ DGE-1745301 (M.J.M.).
